---
title: "Project Outline"
about:
  template: solana
  links:
    - icon: youtube
      text: Youtube
      href: https://www.youtube.com/channel/UCh4BLIfjlJCQ5Lks4nvvwwA
    - icon: github
      text: Github
      href: https://github.com/DanielsHappyWorks/mocap-with-kinect
---

# Introduction

Brief overview of your research topic and area of interest.

# Special Area of Interest

Define and explain your chosen 3D production area.

# Research Context & Literature

Summarize literature and previous work on the topic.

# Research Plan

Methodology and steps for how you’ll carry out the project.

# Artefact Concept

Initial idea of the artefact you will produce to demonstrate your research.

# Timeline

I have already completed some of the work over the summer to figure out what I will be researching.

```{r, include = FALSE}
install.packages("ganttrify",
  repos = c(
    "https://giocomai.r-universe.dev",
    "https://cloud.r-project.org"
  )
)

library("ganttrify")
```

```{r, echo = FALSE, warning = FALSE}
funky_project <- tibble::tribble(
  ~wp, ~activity, ~start_date, ~end_date,
  "Before Semester", "Brainstorming", "2024-06-01", "2024-06-23",
  "Before Semester", "Start Blogging", "2024-06-20", "2024-8-2",
  "Before Semester", "Initial Research", "2024-06-23", "2024-8-2",
)

ganttrify(
  project = funky_project,
  project_start_date = "2024-06",
  by_date = TRUE,
  exact_date = TRUE,
  font_family = "Roboto Condensed"
) +
  ggplot2::ggtitle("Work done over the summer")
```

Now I will focus on creating my artifact that has been defined as part of creating the outline.

```{r, echo = FALSE, warning = FALSE}
funky_project <- tibble::tribble(
  ~wp, ~activity, ~start_date, ~end_date,
  "Blogging", "Write blog posts", "2024-10-01", "2024-12-17",

  "Outline", "Write Outline", "2024-10-01", "2024-10-08",
  "Outline", "Revise Idea", "2024-10-01", "2024-10-02",
  "Outline", "Complie Research", "2024-10-04", "2024-10-06",
  "Outline", "Define Artefact", "2024-10-06", "2024-10-08",
  
  "Progress Report", "Extract animations from kinect", "2024-10-08", "2024-10-13",
  "Progress Report", "Map bones to existing character", "2024-10-13", "2024-10-20",
  "Progress Report", "Figure out presentation style", "2024-10-17", "2024-10-20",
  
  "Alpha", "Add new animations to a game", "2024-10-20", "2024-10-25",
  "Alpha", "Export the game new animations", "2024-10-25", "2024-10-30",
  "Alpha", "Create presentation", "2024-10-30", "2024-11-5",
  
  "Symposium", "Adjust Artifact Based on Alpha", "2024-11-5", "2024-11-30",
  "Symposium", "Export the updated artefact", "2024-11-30", "2024-12-5",
  "Symposium", "Prepare for presentation", "2024-12-5", "2024-12-10",
  
  "Final Documentation", "Create Reflective Journal", "2024-12-10", "2024-12-17",
  "Final Documentation", "Wrap Up Blog", "2024-12-10", "2024-12-17"
)

ganttrify(
  project = funky_project,
  project_start_date = "2024-06",
  by_date = TRUE,
  exact_date = TRUE,
  font_family = "Roboto Condensed"
) +
  ggplot2::ggtitle("Timeline for the project")
```

# Initial Reflections

Early thoughts, goals, and challenges you expect.

# References

List of sources you have consulted for the outline.